>

### 2024-06-02 docs/abstract/_abstract-eupha.qmd
Draft the initial results

**Results:**
Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics ($c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Further groups with high eigenvector centrality were medications for alimentary and metabolism ($c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood ($c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular ($c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics ($c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory ($c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`). Only antidepressants had a positive time trend for both eigenvector centrality and the number of claims.

**Conclusion:**
Eight medications have a high concurrence on a population level. Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes. We recommend constructing a medication claim network to evaluate periodic co-prescription as a public health monitoring procedure.

>>>>

**Results:**
Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Further groups with high eigenvector centrality were medications for alimentary and metabolism ($c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood ($c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular ($c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics ($c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory ($c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`). Only antidepressants had a positive time trend for both eigenvector centrality and the number of claims.

**Conclusion:**
Seven medications have a high concurrence on a population level. Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes. We recommend constructing a medication claim network to evaluate periodic co-prescription as a public health monitoring procedure.

### 2024-06-02 docs/abstract/_abstract-full.qmd
Draft the initial results

**Results:**
Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics (`N05A`, $c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`). Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.

**Discussion:**
Eight medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level. Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes. Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.

>>>>

**Results:**
Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`). Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.

**Discussion:**
Seven medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level. Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes. Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.

### 2024-06-02 docs/article.qmd
Compile as docx
Draft the initial results

format:
  elsevier-pdf:
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear

@@

@@

>>>>

format:
  elsevier-pdf:
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear
  docx: default

@@

### Determining relative importance

Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] is equal to one, a network with similarly connected nodes will have an eigenvector centrality $c_i$ = $\frac{1}{n}$ for each node, where $n$ is the number of nodes. The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where connection $\mathcal{V}_{i, j}$ from node $\mathcal{V}_i$ to node $\mathcal{V}_j$ has the same probability for every node. Per the central limit theorem, the value $\frac{1}{n}$ can be parameterized as a mean of a normal distribution, where all instances of eigenvector centrality will follow the distribution, $c_i \sim \mathcal{N}(\mu, \sigma)$. A one-sample Student's T-test was performed to assess how much each eigenvector centrality differs from the expected values. As such, eigenvector centrality greater than $\frac{1}{n}$ can be considered high, and the value below it can be considered low. The p-values was corrected for a type-I error using Bonferroni method.

@@

tar_load(res_tbl_overview)

n_patient <- prettyNum(res_tbl_overview$total, big.mark = ",", scientific = FALSE)
hi_claim <- res_tbl_overview$overview |> dplyr::slice_max(mean_claim)
lo_claim <- res_tbl_overview$overview |> dplyr::slice_min(mean_claim)

hi_mean <- prettyNum(hi_claim$mean_claim, big.mark = ",")
lo_mean <- prettyNum(lo_claim$mean_claim, big.mark = ",")

IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction. The highest average of prescription claim occurred on `r hi_claim$day`, with $\bar{x}$ = `r hi_mean` [`r hi_claim$sd_claim`]. Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with $\bar{x}$ = `r lo_mean` [`r lo_claim$sd_claim`]. A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in figure [-@fig-period-day]. The cyclical patterns are further explained in our supplementary material. @tbl-desc shows the total number of claim for each medication class alongside the distribution of DDD and its weight.

```{r tbl-desc}
#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by the number of claim

tar_read(res_tbl_stat) %>%
  dplyr::arrange(-n_claim) %>%
  dplyr::mutate(
    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
  ) %>%
  subset(select = c(group, n_claim, mean_sd_dose, median_IQR_dose, range_dose, mean_sd_weight)) %>%
  flextable::flextable() %>%
  flextable::set_header_labels(
    group           = "",
    n_claim         = "Claim",
    mean_sd_dose    = "Mean [SD]",
    median_IQR_dose = "Median [IQR]",
    range_dose      = "Range",
    mean_sd_weight  = "Mean [SD]"
  ) %>%
  flextable::add_header_row(
    values    = c("", "Defined Daily Dose", "Weight"),
    colwidths = c(2, 3, 1),
    top       = TRUE
  ) %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::align(j = 1, align = "left", part = "body") %>%
  #flextable::font(fontname = "Times", part = "all") %>%
  flextable::fontsize(size = 7, part = "all") %>%
  flextable::line_spacing(space = 0.7, part = "all")

```{r fig-period-day}
#| fig-width: 14
#| fig-height: 5
#| fig-cap: Daily cyclical pattern captured on a de-trended data

tar_read(plt_period_day)[[1]]

## Time-series decomposition

Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach. @fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants. SSA-based decomposition separates the trend from its oscillating functions, as shown in the lower half of the plot. The trend explains roughly 90% of the variability, and oscillating functions explain 10%. The first two oscillating functions, F1 and F2, captured most of the variability in a series compared to the rest of the functions.

{{< pagebreak >}}

```{r fig-ssa}
#| fig-width: 16
#| fig-height: 12
#| fig-pos: H
#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach

tar_read(plt_ssa_recon_n_claim)[[17]]

{{< pagebreak >}}

## Relative importance score

```{r fig-hi-eigen}
#| fig-cap: Clusters of medication with a higher eigenvector centrality, implying a higher relative importance in polypharmacy regimens
#| fig-width: 9
#| fig-height: 10

tar_read(plt_hi_eigen)

### 2024-06-02 docs/exec-summary/_descriptive.qmd
Draft an initial report using Elsevier template
Draft the initial results

### Exploratory descriptive analysis

The data was extracted as a daily time-series, which then aggregated into weekly and monthly for exploratory data analysis. The data contains five metrics, including the number of daily medication claims, the number of daily patients, claim-to-patient ratio, and eigenvector centrality. For each metrics in each dataset, univariate descriptive analysis was performed by calculating the statistical summary to describe the centrality and spread. Mean, median, standard deviation, and interquartile range were reported to evaluate the distribution. The data is split into pre-COVID-19 and during COVID-19 period, and mean difference was calculated using Welch's T-Test. For visual examination, pair plots were generated for each medication group. The correlations between metrics were calculated by considering pre-COVID-19, during COVID-19, and the overall association. Daily, weekly, and monthly time-series were also plotted and grouped by medications. Classical and seasonal-trend decomposition using LOESS (STL) were performed to extract decomposed trend for further visual evaluation. Each dataset was then detrended by performing a first-degree differencing, i.e. taking the differences between $x_t$ and $x_{t-1}$.

>>>>

::: {.content-visible unless-meta="in.article"}
### Exploratory descriptive analysis
:::

The data was extracted as a daily time-series, which then aggregated into weekly and monthly for exploratory data analysis. The data contains five metrics, including the number of daily medication claims, the number of daily patients, claim-to-patient ratio, and eigenvector centrality. For each metrics in each dataset, univariate descriptive analysis was performed by calculating the statistical summary to describe the centrality and spread. Mean, median, standard deviation, and interquartile range were reported to evaluate the distribution.

::: {.content-visible unless-meta="in.article"}
The data is split into pre-COVID-19 and during COVID-19 period, and mean difference was calculated using Welch's T-Test. For visual examination, pair plots were generated for each medication group. The correlations between metrics were calculated by considering pre-COVID-19, during COVID-19, and the overall association. Daily, weekly, and monthly time-series were also plotted and grouped by medications. Classical and seasonal-trend decomposition using LOESS (STL) were performed to extract decomposed trend for further visual evaluation. Each dataset was then detrended by performing a first-degree differencing, i.e. taking the differences between $x_t$ and $x_{t-1}$.
:::
